Lens Modeling in \sw

### 2013-09-10 text/tex/outlook.tex
more edits
labels

As seen in \secref{tests.1}, volunteers fail mostly in two situations:
when to identify an arclike structre while placing the points
and in 5 image configurations, that are quite symmetric, then to identify the correct ordering of the points.

@@

>>>>

As seen in \secref{tests.t1}, volunteers fail mostly in two situations:
when to identify an arclike structre while placing the points
and in 5 image configurations, that are quite symmetric, then to identify the correct ordering of the points.

@@

Lenses with more than one maximum can be allowed for.  See Figure 5c
in \citep{2001ApJ...557..594R} and Figure 4b in
\cite{2003ApJ...590...39K}.

Supply several images from several bands.
